---
title: 'Analyses Experiment'
author: 
output: 
  github_document:
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center", cache = FALSE,
                      fig.path=('../../../report/figures/'))
library(rmarkdown)
```

# Scripts


# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
```

# Pre-Registered Analyses

```{r "data for analyses"}
load(here("data/intermediate/cleaned_experiment.RData"))

source(here("src/analysis/experiment/scaling.R"))
kbl(scale, booktabs =T, caption = "\\label{tab:scale}Reliable Scales") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "4cm")
rm(scale)

source(here("src/analysis/experiment/data-for-analyses.R"))
```

## Descriptive Results
```{r "descriptive-results", echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(DV1:DV3, compromise, outcome) %>%
  pivot_longer(cols = DV1:DV3,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `DV1` = "DV: Trust",
                      `DV2` = "DV: Credibility",
                      `DV3` = "DV: Representation"),
         outcome = recode(outcome, 
                           `stalled` = "Coalition talks stalled", 
                           `negotiation` = "Parties go to negotiation phase"),
         compromise = recode(compromise,
                             `yes` = "Party compromised",
                             `no` = "Party remained steadfast")) %>%
  unite(treat, compromise, outcome, sep = " - ") %>%
  group_by(treat, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = treat, 
             y =means, label = means,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~.) +
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Reputational Cost of Compromise") +
  theme_ipsum() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

## Balance Checks

The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Living Place`, `Birth Place`, `Age`, `Political Knowledge`, `Political Interest`, and `Ideology`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

```{r "balance-checks", fig.height=10, fig.width=10}
source(here("src/analysis/experiment/balance-test.R"))
df
```

## Manipulation Checks

```{r "mc", fig.height=10, fig.width=10}
source(here("src/analysis/experiment/MC.R"))
p0

pa
pb
pc_2b/ pc_2a + plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')
pd
```

## Steadfast Hypothesis & Outcome Hypothesis
```{r "h1", fig.align="center", fig.height=5, fig.width=10}
source(here("src/analysis/experiment/h1_exp.R"))
p1
```

## Compromise Hypothesis
```{r "h3", fig.align="center", fig.height=5, fig.width=10}
source(here("src/analysis/experiment/h3_exp.R")) 
p2

source(here("src/analysis/experiment/h3_exp_int.R")) 
p2_int
```

## Principled Hypothesis
```{r "h4", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/experiment/h4_exp.R")) #pooled?
p3b / p3a + plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')

p3_2b/ p3_2a + plot_layout(guides = 'collect')  & theme(legend.position = 'none')
```

## Mutual Trust Hypothesis
```{r "h5", fig.align="center", fig.height=7, fig.width=10}
source(here("src/analysis/experiment/h5_exp.R")) #pooled?
p4

p4_2
```

# Robust  
Results for those who know who is in the actual coalition negotiations

```{r "robust", fig.align="center", fig.height=7, fig.width=10}
source(here("src/analysis/experiment/robust.R")) #pooled?
pa
pb
pc_2b/ pc_2a + plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')
pd
```

# Exploration

```{r "h45-direct", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/experiment/exploration_h45.R")) 
p45d1 + p45d2 + p45d3 +
  plot_layout(guides = 'collect')  & theme(legend.position = 'bottom')

p34e
```

```{r "effect-on-compromise-attitude", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/experiment/exploration_compromise_attitude.R")) 
p_ca
```


```{r "effects-per-party", fig.align="center", fig.height=8, fig.width=18}
source(here("src/analysis/experiment/exploration_h1_party.R")) 
p1_e

source(here("src/analysis/experiment/exploration_h3_party.R")) 
p2_e

source(here("src/analysis/experiment/exploration_h4_party.R"))
p4a_e1 + p4a_e2 +
  plot_annotation(title = 'Principledness (2)')

p4b_e1 + p4b_e2 +
  plot_annotation(title = 'Principledness (1)')

source(here("src/analysis/experiment/exploration_h5_party.R"))
p5_e1 + p5_e2 +
  plot_annotation(title = 'Mutual Trust')
```

```{r "explor-pol-mod", fig.align="center", fig.height=8, fig.width=18}
source(here("src/analysis/experiment/exploration_pol_mod.R"))
mod_a
mod_b
mod1
mod2
mod3
mod4
mod5
mod6
mod7
```