---
title: 'Analyses'
author: 
output: 
  github_document:
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
options(scipen = 1, digits = 2)
library(rmarkdown)
```

# Scripts


# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
```

# Pre-Registered Analyses

```{r "data for analyses"}
load(here("treatment-experiment/data/intermediate/cleaned_experiment.RData"))
```

Next, we automatically extract a `.md` file for the online appendix, as well as a  latex table for the manuscript. 
We are using jinja2 template [src/analysis/table_descriptives.tex.j2](table.tex.j2) which is called with a json string containing the data.
To replicate, make sure `env/bin/pip install -U j2cli` is installed via your command line.

```{r "Table with Descriptives", eval=F}
source(here("src/analysis/descriptive-information-overview.R"))
table2 <- knitr::kable(descr, digits=2)
fn <- here("report/figures/table_descriptives.tex")
cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
cat(table2, file=fn, sep="\n", append=T)

methodnames <- setNames(as.list(descr$Variables), descr$Variables)
table <- purrr::map(descr, .f= ".") 
#render_j2(here("src/analysis/table_descriptives.tex.j2"), here("report/figures/table_descriptives.tex"),
#          data=list(data=table, methods=methodnames))
rm(descr, methodnames, table, fn, table2)
```

## Descriptive Results
```{r "descriptive-results", echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(MC, AC, time, treatment) %>%
  pivot_longer(cols = MC:time,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       MC = "Manipulation Checks ",
                       AC = "Attention Check",
                       time = "Time"),
         value = as.numeric(value),
         treatment = if_else(treatment=="insta", "Instagram Treatment", "Textual Treatment")) %>%
  group_by(treatment, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.96 * stdev),
         upper = means + (1.96 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = treatment, 
             y =means, label = means,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~.) +
  labs(y = "", 
       x = "", title = "Do Visual Experimental Treatments Improve Respondent's Engagement?") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

## Balance Checks

The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Living Place`, `Birth Place`, `Age`, `Political Knowledge`, `Political Interest`, and `Ideology`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

```{r "balance-checks", fig.height=10, fig.width=10}
source(here("treatment-experiment/src/analysis/balance-test.R"))
df
```

##  Hypotheses 
```{r "hs", fig.align="center", fig.height=10, fig.width=15}
source(here("treatment-experiment/src/analysis/hs.R"))
h
```

## Exploration: Interactions Age & Digital Literacy with Treatment
```{r "exp", fig.align="center", fig.height=15, fig.width=10}
source(here("treatment-experiment/src/analysis/exp.R"))
he
```