---
title: 'Prepare Observational Data'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
  - [CSES Data](#cses-data)
  - [DPES Data](#dpes-data)
  - [BES Data](#bes-data)
- [Missing Values](#missing-values)
  - [Austria](#austria)
  - [France](#france)
  - [Germany](#germany)
  - [Italy](#italy)
  - [The Netherlands](#the-netherlands)
  - [Great Britain](#great-britain)
- [Save Data for Analysis](#save-data-for-analysis)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Independent Variable](#independent-variable)
  - [Control Variables](#control-variables)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F, results='hide'}
rm(list=ls())
source(here::here("src/lib/functions.R"))
renv::snapshot()
```

## Tidy Data

### CSES Data
Data can be downloaded [here](https://cses.org/data-download/download-data-documentation/), and is saved as `.RDS` file to save space.
```{r "tidy cses", message=FALSE, warning=FALSE}
source(here("src/data-processing/tidy_cses.R"))
```

### DPES Data

Data can be downloaded [here](https://easy.dans.knaw.nl/ui/datasets/id/easy-dataset:101156), and is saved as `.RDS` file to save space.

```{r "tidy dpes", message=FALSE, warning=FALSE}
source(here("src/data-processing/tidy_dpes.R"))
```

### BES Data

Data can be downloaded [here](https://www.britishelectionstudy.com/data/#.X7yS5tso-F0), and is saved as `.RDS` file to save space.

```{r "tidy bes", message=FALSE, warning=FALSE}
source(here("src/data-processing/tidy_bes.R"))
```

## Missing Values
As pre-registered [here](https://osf.io/nt6ra/?view_only=b84cde8bd47f4e94ac529b088542b8d0), we employ the following criteria:

- If 10\% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
- If 11\% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.


### Austria
```{r "missing aut", message=FALSE, warning=FALSE}
covar <- c("Trust", "Willingness to Accept Compromise","Party ID",
           "Political Interest", "Left-Right Self-Placement",
           "Government Performance","Gender", "Age","Education", "Income")
aut <- d %>%
  filter(country=="Austria")
tibble(Covariate = covar,
       Percentage =c(round(sum(is.na(aut$trust))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$wtac))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$pid))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$political_interest))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$rile_selfplacement))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$gov_performance))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$gender))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$age))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$education))/prod(dim(aut)[1]),2),
                     round(sum(is.na(aut$income))/prod(dim(aut)[1]),2)))
```
We recode the missing values of `trust` and `willingness to accept compromise` variables to the mean value of the respective variables. 
For the categorical variables `party id` and `government performance` we use the median value. 

```{r "missing aut2", message=FALSE, warning=FALSE}
aut <- aut %>%
 mutate(trust = replace_na(trust, mean(trust, na.rm=T)),
        wtac = replace_na(wtac, mean(wtac, na.rm=T)),
        pid = replace_na(pid, "No Partisan ID"),
        gov_performance = replace_na(gov_performance, "Dissatisfied"),
        missing_gov_performance = 0,
        missing_trust = 0,
        missing_wtac = 0,
        missing_pid = 0,
        missing_education = 0,
        missing_income = 0,
        missing_age = 0,
        missing_gender = 0,
        missing_rile_selfplacement = 0)
```

### France
```{r "missing fr", message=FALSE, warning=FALSE}
fr <- d %>%
  filter(country=="France")
tibble(Covariate = covar,
       Percentage =c(round(sum(is.na(fr$trust))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$wtac))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$pid))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$political_interest))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$rile_selfplacement))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$gov_performance))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$gender))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$age))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$education))/prod(dim(fr)[1]),2),
                     round(sum(is.na(fr$income))/prod(dim(fr)[1]),2)))
```
We recode the missing values of `trust`, `willingness to accept compromise`, `left-right self-placement`, and `education` variables to the mean value of the respective variables. 
For the categorical variables `party id` and `government performance`, we use the median value. 

```{r "missing fr2", message=FALSE, warning=FALSE}
fr <- fr %>%
 mutate(trust = replace_na(trust, mean(trust, na.rm=T)),
        wtac = replace_na(wtac, mean(wtac, na.rm=T)),
        pid = replace_na(pid, "Partisan ID"),
        education = replace_na(education, round(mean(education, na.rm=T),0)),
        rile_selfplacement = replace_na(rile_selfplacement, 
                                        mean(rile_selfplacement, na.rm = T)),
        gov_performance = replace_na(gov_performance, "Dissatisfied"),
        missing_gov_performance = 0,
        missing_rile_selfplacement =  0,
        political_interest = replace_na(political_interest, "Not Interested"),
        missing_trust = 0,
        missing_wtac = 0,
        missing_pid = 0,
        missing_education = 0,
        missing_income = 0,
        missing_gender = 0,
        missing_age = 0)
```

### Germany
```{r "missing de", message=FALSE, warning=FALSE}
de <- d %>%
  filter(country=="Germany")
tibble(Covariate = covar,
       Percentage =c(round(sum(is.na(de$trust))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$wtac))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$pid))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$political_interest))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$rile_selfplacement))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$gov_performance))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$gender))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$age))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$education))/prod(dim(de)[1]),2),
                     round(sum(is.na(de$income))/prod(dim(de)[1]),2)))
```

We recode the missing values of `trust`, `willingness to accept compromise`, `left-right self-placement`, and `education` variables to the mean value of the respective variables. 
For the categorical variable `party id` and `government performance`, we use the median value. 

```{r "missing de2", message=FALSE, warning=FALSE}
de <- de %>%
 mutate(trust = replace_na(trust, mean(trust, na.rm=T)),
        wtac = replace_na(wtac, mean(wtac, na.rm=T)),
        education = replace_na(education, round(mean(education, na.rm=T),0)),
        pid = replace_na(pid, "No Partisan ID"),
        rile_selfplacement = replace_na(rile_selfplacement, 
                                        mean(rile_selfplacement, na.rm = T)),
        political_interest = replace_na(political_interest, "Not Interested"),
        gov_performance = replace_na(gov_performance, "Satisfied"),
        missing_gov_performance = 0,
        missing_trust = 0,
        missing_wtac = 0,
        missing_pid = 0,
        missing_education = 0,
        missing_income = 0,
        missing_age = 0,
        missing_gender = 0,
        missing_rile_selfplacement = 0)
```

### Italy
```{r "missing it", message=FALSE, warning=FALSE}
it <- d %>%
  filter(country=="Italy")
tibble(Covariate = covar,
       Percentage =c(round(sum(is.na(it$trust))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$wtac))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$pid))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$political_interest))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$rile_selfplacement))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$gov_performance))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$gender))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$age))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$education))/prod(dim(it)[1]),2),
                     round(sum(is.na(it$income))/prod(dim(it)[1]),2)))
```

We recode the missing values of `trust` and `willingness to accept compromise` variables to the mean value of the respective variables. 
For the categorical variables `party id`, `government performance`, and `political interest`, we use the median value. 

```{r "missing it2", message=FALSE, warning=FALSE}
it <- it %>%
 mutate(trust = replace_na(trust, mean(trust, na.rm=T)),
        wtac = replace_na(wtac, mean(wtac, na.rm=T)),
        pid = replace_na(pid, "No Partisan ID"),
        political_interest = replace_na(political_interest, "Not Interested"),
        gov_performance = replace_na(gov_performance, "Dissatisfied"))
```

We recode the missing values of the variable `left-right self-placement` to `5` and include the variable `missing_rile_selfplacement` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).

```{r "missing it3", message=FALSE, warning=FALSE}
it <- it %>%
 mutate(missing_rile_selfplacement = ifelse(is.na(rile_selfplacement), 1, 0),
        rile_selfplacement = replace_na(rile_selfplacement, 5),
        education = replace_na(education, round(mean(education, na.rm=T),0)),
        missing_trust = 0,
        missing_wtac = 0,
        missing_pid = 0,
        missing_education = 0,
        missing_income = 0,
        missing_age = 0,
        missing_gender = 0,
        missing_gov_performance = 0)
```

### Netherlands
```{r "missing nl", message=FALSE, warning=FALSE}
tibble(Covariate = covar,
       Percentage =c(round(sum(is.na(nl$trust))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$wtac))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$pid))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$political_interest))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$rile_selfplacement))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$gov_performance))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$gender))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$age))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$education))/prod(dim(nl)[1]),2),
                     round(sum(is.na(nl$income))/prod(dim(nl)[1]),2)))
```

We recode the missing values of the `income` variable to its mean value. 
For the categorical variable `political interest`, we use the median value. 

```{r "missing nl2", message=FALSE, warning=FALSE}
nl <- nl %>%
 mutate(income = replace_na(income, round(mean(income, na.rm=T),0)),
        political_interest = replace_na(political_interest, "Not Interested"),
        gender = replace_na(gender, "Male"))
```

We recode the missing values of the variables `Trust` and `Willingness to Accept Compromise`, to `3` and include the variables `missing_trust` and `missing_wtac` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Party ID`, to `No Party ID` and include the variable `missing_pid` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Government Performance`, to `Satisfied` and include the variable `missing_gov_performance` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Education`, to `4` and include the variable `missing_education` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Left-Right Self-Placement` to `5` and include the variable `missing_rile_selfplacement` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).

```{r "missing nl3", message=FALSE, warning=FALSE}
nl <- nl %>%
 mutate(missing_trust = ifelse(is.na(trust), 1, 0),
        trust = replace_na(trust, 3),
        missing_wtac = ifelse(is.na(wtac), 1, 0),
        wtac = replace_na(wtac, 3),
        missing_pid = ifelse(is.na(pid), 1, 0),
        pid = replace_na(pid, "No Partisan ID"),
        missing_education = ifelse(is.na(education), 1, 0),
        education = replace_na(education, 4),
        missing_rile_selfplacement = ifelse(is.na(rile_selfplacement), 1, 0),
        rile_selfplacement = replace_na(rile_selfplacement, 5),
        missing_gov_performance = ifelse(is.na(gov_performance), 1, 0),
        gov_performance = replace_na(gov_performance, "Satisfied"),
        missing_income = 0,
        missing_age = 0,
        missing_gender = 0)
```

### Great Britain
```{r "missing uk", message=FALSE, warning=FALSE}
tibble(Covariate = covar,
       Percentage =c(round(sum(is.na(uk$trust))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$wtac))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$pid))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$political_interest))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$rile_selfplacement))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$gov_performance))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$gender))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$age))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$education))/prod(dim(uk)[1]),2),
                     round(sum(is.na(uk$income))/prod(dim(uk)[1]),2)))
```

We recode the missing values of the variables `Trust`, `Willingness to Accept Compromise`, and `Income` to `3` and include the variables `missing_trust`, `missing_wtac`, `missing_income` to the data, indicating whether the response on the covariate was missing (value of one) or not (value of 0).
We recode the missing values of the variable `Left-Right Self-Placement` to `5` and include the variable `missing_rile_selfplacement` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
e recode the missing values of the variable `Government Performance`, to `Dissatisfied` and include the variable `missing_gov_performance` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Party ID` and `Gender` to respecively `No Party ID` and `Female` and include the variables `missing_pid` and `missing_gender` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Education`, to `4` and include the variable `missing_education` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).
We recode the missing values of the variable `Age` to the mean and include the variable `missing_age` to the data, indicating whether the response on the covariate was missing (value of 1) or not (value of 0).

```{r "missing uk2", message=FALSE, warning=FALSE}
uk <- uk %>%
 mutate(missing_trust = ifelse(is.na(trust), 1, 0),
        trust = replace_na(trust, 3),
        missing_wtac = ifelse(is.na(wtac), 1, 0),
        wtac = replace_na(wtac, 3),
        missing_pid = ifelse(is.na(pid), 1, 0),
        pid = replace_na(pid, "No Partisan ID"),
        missing_gender = ifelse(is.na(gender), 1, 0),
        gender = replace_na(gender, "Female"),
        missing_age = ifelse(is.na(age), 1, 0),
        age = replace_na(age, round(mean(age, na.rm=T),0)),
        missing_income = ifelse(is.na(income), 1, 0),
        income = replace_na(income, 3),
        missing_education = 0,
        education = replace_na(education, round(mean(education, na.rm=T),0)),
        political_interest = replace_na(political_interest, "Not Interested"),
        missing_rile_selfplacement = ifelse(is.na(rile_selfplacement),1, 0),
        rile_selfplacement = replace_na(rile_selfplacement, 5),
        missing_gov_performance = ifelse(is.na(gov_performance), 1, 0),
        gov_performance = replace_na(gov_performance, "Dissatisfied"))
```

## Save Data for Analysis
```{r "compile data", message=FALSE, warning=FALSE}
d <- aut %>%
  add_row(fr) %>%
  add_row(de) %>%
  add_row(it) %>%
  add_row(nl) %>%
  add_row(uk)
rm(aut, de, fr, it, nl, uk, covar)
```

## Visualization of Data

### Dependent Variable
```{r "dv", echo=F, message=FALSE, warning=FALSE}
d %>%
  ggplot(mapping = aes(y = country, x = trust)) +
  geom_boxplot(fill = "seagreen", alpha = .2) +
  labs(y = "", x = "Strongly disagree (1) - Strongly agree (5)", title = "Most politicians are trustworthy") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) 
```

### Independent Variable
```{r "iv", echo=F, message=FALSE, warning=FALSE}
d %>%
  ggplot(mapping = aes(y = country, x = wtac)) +
  geom_boxplot(alpha = .2, fill = "seagreen") +
  labs(y = "", x = "Strongly Agree (1) - Strongly Disagree (5)", title = "Compromise is selling out principles") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```

### Control Variables
```{r "controls", echo=F, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
d %>%
  dplyr::select(country, Gender = gender, `Party ID` = pid, 
         `Political Interest` = political_interest,
         `Government Performance` = gov_performance) %>%
  pivot_longer(cols = Gender:`Government Performance`) %>%
  group_by(country, name, value) %>%
  summarise(n = n()) %>%
  ggplot(mapping = aes(x = country, y = n, group = value, fill = value)) +
  geom_col(alpha = .2, position = position_dodge()) +
  facet_wrap(.~name, scales = "free") +
  scale_fill_manual(values = c("seagreen", "seagreen","seagreen",
                               "violet","seagreen", "violet", "violet", 
                               "violet")) +
  labs(x = "", y = "Count", title = "Categorical Control Variables") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank(), #edit the legend
        legend.position = "bottom",
        legend.box="vertical",
        axis.text.x=element_text(color = "black", size=11, 
                                 angle=30, vjust=.8, hjust=0.8))
```

```{r "controls2", echo=F, message=FALSE, warning=FALSE, fig.width=10, fig.height=7}
d %>%
  dplyr::select(country, Age = age, Income = income, 
         Education = education, 
         `Left-Right Self-Placement` = rile_selfplacement) %>%
  pivot_longer(cols = Age:`Left-Right Self-Placement`) %>%
  ggplot(mapping = aes(y = country, x = value)) +
  geom_boxplot(alpha = .2, fill = "seagreen") +
  facet_wrap(.~ name, scales = "free") +
  labs(y = "", x = "Mean Values", title = "Continuous Control Variables") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x=element_text(color = "black", size=11, 
                                 angle=30, vjust=.8, hjust=0.8))
```

### Correlations Matrix
```{r "correlation-matrix", echo=F, message=T, warning=T, fig.width=8, fig.height=8}
d %>%
  dplyr::select(`Political Trust` = trust,
         `Willingness to Accept Compromises` = wtac,
         Gender = gender, 
         `Party ID` = pid, 
         `Political Interest` = political_interest,
         Age = age, 
         Income = income, 
         Education = education, 
         `Left-Right Self-Placement` = rile_selfplacement,
         `Government Performance`= gov_performance) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c("violet", "white", "seagreen"),
  title = "Correlalogram for Variables under Study"
)
```