---
title: "Preprare Data"
output:
  github_document:
  toc: yes
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(printr)
library(rmarkdown)
```
# Analysis
- [Set Up](#set-up)
- [Analyses](#analysis)
  - [Pre-Registered](#pre-registered)
  - [Exploratory](#exploratory)

## Set-up
```{r}
rm(list=ls())
source("../lib/functions.R")
d <- readRDS("../../data/intermediate/observational_data.RDS")
```

## Analyses

### Pre-Registered
The code below demonstrate the OLS regression predicting the level of political trust by willingness to accept compromises.
Next to the control variables, it includes country dummies and dummies indicating whether more than ten percent of the values where missing.

```{r, message=F, warning=F, fig.width=10, fig.height=7}
analysis <- d %>%
  dplyr::select(trust, wtac, political_interest, rile_selfplacement,
         gov_performance, pid, gender, age, education, income, country,
         missing_trust, missing_wtac, missing_rile_selfplacement,
         missing_gov_performance, missing_pid, missing_gender, 
         missing_age, missing_education, missing_income) 
m <- stats::lm(formula = trust ~ wtac + factor(political_interest) +
                  rile_selfplacement + factor(gov_performance) + 
                 factor(pid) + factor(gender) + age +
                  education + income + factor(country) + 
                  factor(missing_trust) + factor(missing_wtac) +
                  factor(missing_rile_selfplacement) + factor(missing_pid) +
                  factor(missing_gender) + factor(missing_age) + 
                  factor(missing_education) + factor(missing_income),
                data = analysis)
```

```{r, echo = F, message=F, warning=F, fig.width=10, fig.height=7}
ggcoefstats(
  x = tidy(m)[2:10,],
  point.args = list(color = "seagreen", size = 3, shape = 15, alpha = .75),
  vline.args = list(size = 1, color = "darkgrey", linetype = "dotdash"),
  statistic = "t",
  stats.label.color = "seagreen",
  only.significant = TRUE,
  package = "palettesForR",
  palette = "Inkscape",
  title = "Political Trust Predicted by Willingness to Compromise",
  ggtheme = theme_minimal(),
  ggstatsplot.layer = F) + # note the order in which the labels are entered
  scale_y_discrete(labels = c("Willingness to Accept Compromise", 
                              "Not Politically Interested", 
                              "Left-Right Self-Placement",
                              "Satisfied with Government Performance",
                              "Partisan ID",
                              "Male",
                              "Age",
                              "Education", "Income")) +
  labs(x = "Regression Coefficients", y = NULL) 
```

The beta-coefficient of Willingness to Accept Compromise is negative and statistically significant, as hypothesized in [our Pre-Analysis Plan](https://osf.io/h29j3).
The coefficient of -0.15 is however a small effect. 
It indicates that when Willingness to Accept Compromise goes up by 1 -- i.e. answering `rather no` instead of `not at all` with the statement _What people call compromise in politics is really just selling out on one's principles._ -- the the level of trust in politicians goes down by 0.15.
Trust in politicians is a five-point scale, where 1 indicates completely disagreeing with the statement _Most politicians are trustworthy_ and 5 indicates that completely agrees with the statement.

Because we pooled the data of various countries, the graph below demonstrate the country differences. 
This graph demonstrates that the hypothesized relationship is strongest in the Netherlands, and exactly average in Germany.
In Italy and France, the data shows no (significant) relationship between trust in politicians and willingness to compromise.
The relationship between political trust and willingness to accept compromise in Great Britain is positive.

```{r, echo = F, message=F, warning=F, fig.width=10, fig.height=7}
ggcoefstats(
  x = tidy(m)[10:14,],
  point.args = list(color = "seagreen", size = 3, shape = 15, alpha = .75),
  vline.args = list(size = 1, color = "darkgrey", linetype = "dotdash"),
  statistic = "t",
  only.significant = TRUE,
  stats.label.color = "seagreen",
  title = "Political Trust Predicted by Willingness to Compromise",
  subtitle = "Country Differences",
  ggtheme = theme_minimal(),
  ggstatsplot.layer = FALSE) + # note the order in which the labels are entered
  scale_y_discrete(labels = c("France", 
                              "Germany", 
                              "Great Britain",
                              "Italy",
                              "The Netherlands")) +
  labs(x = "Regression Coefficients", y = NULL)
```

Moreover, we have imputed the missing values using the _Green \& Gerber formula_ (Green \& Gerber 2008). 
To demonstrate whether the dichotomous variables indicating whether the respondents' value was missing are different from the respondents' who have completed the question, the graph below demonstrates the coefficients of the `missing dummies`.
The graph shows that only for the variables `age` and `trust` the imputed values elicit a different effect from the non-imputed ones. 

```{r, echo=F, message=F, warning=F, fig.width=10, fig.height=7}
ggcoefstats(
  x = tidy(m)[15:22,],
  point.args = list(color = "seagreen", size = 3, shape = 15, alpha = .75),
  vline.args = list(size = 1, color = "darkgrey", linetype = "dotdash"),
  statistic = "t",
  only.significant = TRUE,
  stats.label.color = "seagreen",
  title = "Political Trust Predicted by Willingness to Compromise",
  subtitle = "Missing Values",
  ggtheme = theme_minimal(),
  ggstatsplot.layer = FALSE) + # note the order in which the labels are entered
  scale_y_discrete(labels = c("Trust", 
                              "Willingness to Accept Compromise", 
                              "Left-Right Self-Placement",
                              "Party ID", "Gender", "Age",
                              "Education", "Income")) +
  labs(x = "Regression Coefficients", y = NULL)

```





### Exploratory