---
title: "Results Observational Study"
output:
  github_document:
  toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(rmarkdown)
```

# Analysis
- [Set Up](#set-up)
- [Analyses](#analysis)
  - [Pre-Registered](#pre-registered)
  - [Exploratory](#exploratory)

## Set-up
```{r "set-up", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
load(here("data/intermediate/observational_data.Rdata"))
```

## Analyses

### Pre-Registered
The code below demonstrate the OLS regression predicting the level of political trust by willingness to accept compromises.
Next to the control variables, it includes country dummies and dummies indicating whether more than ten percent of the values where missing.

```{r "h1-obs", message=F, warning=F, fig.width=10, fig.height=7}
source(here("src/analysis/h1_obs.R"))
h1
```

The beta-coefficient of Willingness to Accept Compromise is positive and statistically significant, as hypothesized in [our Pre-Analysis Plan](https://osf.io/h29j3).
The coefficient of 0.15 is however a small effect. 
It indicates that the higher one's willingness to accept compromise, the higher one's trust in politicians.
More precisely, it means that when Willingness to Accept Compromise goes up by 1 -- i.e. answering `rather yes` instead of `completely agree` with the statement _What people call compromise in politics is really just selling out on one's principles._ -- the the level of trust in politicians goes up by 0.15.
Trust in politicians is a five-point scale, where 1 indicates completely disagreeing with the statement _Most politicians are trustworthy_ and 5 indicates that completely agrees with the statement.

Because we pooled the data of various countries, the graph below demonstrate the country differences. 
The Netherlads is the reference category.
This graph demonstrates that all countries, but particularly France, Germany, Great Britain, and Italy, are statistically different from the Netherlands.

```{r "robust1", echo = F, message=F, warning=F, fig.width=10, fig.height=7}
r1
```

To make sure the effect is not driven by any particular country, the graphs below show that for all countries, the coefficient is positive.
Moreover, except for Italy, the coefficient is statistically significant too.
This indicates that the effects found in the pooled analysis are not driven by any specific country.
```{r "robust2", echo = F, message=F, warning=F, fig.width=12, fig.height=20}
source(here("src/analysis/robust_obs.R"))
(p1 + p2) /( p3 + p4)/ ( p5 + p6)
```

Moreover, we have imputed the missing values using the _Green \& Gerber formula_ (Green \& Gerber 2008). 
To demonstrate whether the dichotomous variables indicating whether the respondents' value was missing are different from the respondents' who have completed the question, the graph below demonstrates the coefficients of the `missing dummies`.
The graph shows that only for the variables `age` and `trust` the imputed values elicit a different effect from the non-imputed ones. 

```{r "robust4", echo=F, message=F, warning=F, fig.width=10, fig.height=7}
r2
```

The result show that particularly the imputed missing values for `trust` and `age` seem to elicit an effect in the regression results.
To check the robustness of the analysis, we therefore have also ran the analysis excluding the observations where `trust` and `age` have been imputed.
As the visualization below demonstrates, this does not change the coefficient of `willingness to accept compromise`.

```{r "robust5", echo = F, message=F, warning=F, fig.width=10, fig.height=7}
r3
```

### Replication Full CSES Round 5
```{r "cses5", echo = F, message=F, warning=F, fig.width=10, fig.height=7}
load(here("data/intermediate/cses_round5.Rdata"))
source(here("src/analysis/replication.R"))
rep
```

